---
title: "CICERON 120 PAX - MADRID/BARCELONA"
author: "Malin Berggren Lundell"
date: 'January 2020'
output:
 
  html_document:
    css: FORMATO.css
    highlight: textmate
    theme: cosmo
    toc: yes
    toc_float: yes
---

<script> 
    $(document).ready(function() { 
    $head = $('#header'); 
    $head.prepend('<A href = https://www.cuttingedge-events.com><img src ="LOGO.png" width="150" vspace="50" align="right"></A>') 
    }); 
</script> 



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```


```{r libraries}
library(readxl)
library(dplyr)
library(knitr)
library(timevis)

```


# **BARCELONA**

## **Parador Cardona**

With a magical setting inside a 9th-century castle and boasting a 2nd-century tower, this Parador is straight out of fairytale and has panoramic views over the Catalonian countryside.

Interiors are faithful to the Cardona's history with Medieval styling complementing the castles vaulted ceilings, stone walls and gorgeous courtyards.

Dine in the Cardona's Medieval dining room which is fit for a king. Enjoy regional specialities which source the freshest local produce for an authentic taste of Catalonia.

Bedrooms have charming canopy beds and gothic features . Furnishings are inspired from the Catalan Medieval period and are highlighted by theatrical lighting and rich fabrics.

  * The hotel has 54 rooms. They have different sizes so we can have them in double or triple occupation.
  * It is located 100km from Barcelona Airport



<img src = "https://q-cf.bstatic.com/images/hotel/max1024x768/744/7440861.jpg">

<img src = "https://r-cf.bstatic.com/images/hotel/max1024x768/208/20880946.jpg">

<img src = "https://q-cf.bstatic.com/images/hotel/max1024x768/743/7437794.jpg">

<img src = "https://r-cf.bstatic.com/images/hotel/max1024x768/253/25318881.jpg">

<br>
<br>

## **Hostal Ampuries**

Hostal Empúries 4* is set in a restored building overlooking the Mediterranean from a secluded beach. It is located nearby Empuries Archeological Site and is a 5-minute drive from L’Escala, on the Costa Brava.

The charming rooms at Hostal Empúries all come with a work desk and include en suite bathrooms. 

  * The hotel has 53 rooms. They have different sizes the most of them would be double/twin but some of them can be triple or cuadruple
  * It has the LEED certificate (Lidership Europe Enviromental Design)
  * It has a meeting room with a capacity for 140pax
  * It is located 166km from Barcelona Airport 
  
<img src = "https://r-cf.bstatic.com/images/hotel/max1024x768/501/50149706.jpg">  

<img src = "https://r-cf.bstatic.com/images/hotel/max1024x768/154/154295315.jpg">

<img src = "https://q-cf.bstatic.com/images/hotel/max1024x768/775/77515504.jpg">

<img src = "https://q-cf.bstatic.com/images/hotel/max1024x768/181/18161205.jpg">

<img src = "https://q-cf.bstatic.com/images/hotel/max1024x768/154/154301268.jpg">


<br>
<br>

## **Hotel Món Sant Benet**


Hotel Món Sant Benet has modern facilities in the Medieval Monastery of Sant Benet de Bages. 

All rooms include a private terrace with views of the monastery and the Sant Llorenç del Munt i l'Obac Natural Park. They include a private bathroom with a bath and shower, air conditioning, heating, a flat-screen TV, and a minibar. All reservations include a visit to the Monastery, reservation in advance is needed.

Hotel Món Sant Benet has 3 restaurants, among which stands out the L'Ó, awarded a Michelin Star, offering creative and healthy versions of traditional cuisine.

  * The hotel has 87 rooms. 
  * It is located 70km from Barcelona Airport
  * It has a small conference centre, the plenary room will have capacity for the group in theater style.

<img src = "https://r-cf.bstatic.com/images/hotel/max1024x768/207/207301236.jpg">  

<img src = "https://q-cf.bstatic.com/images/hotel/max1024x768/439/43939283.jpg">

<img src = "https://r-cf.bstatic.com/images/hotel/max1024x768/706/7063303.jpg">

<img src = "https://r-cf.bstatic.com/images/hotel/max1024x768/439/43939225.jpg">

<br>
<br>

## **Hotel Peralada**


Hotel Peralada Wine Spa and Golf has rooms with views over the resort golf course.  The hotel also offers an outdoor seasonal pool.

Rooms at the Peralada are modern and feature bright décor. All rooms have free Wi-Fi access.

A range of treatments and massages are available in the Peralada’s wine spa.

The Olivera restaurant features a terrace and serves Mediterranean cuisine. 

  * The hotel has 56 rooms. They have different sizes so we can have them in double or triple occupation.
  * It is located 165km from Barcelona Airport


<img src = "https://q-cf.bstatic.com/images/hotel/max1024x768/828/82851863.jpg">  

<img src = "https://q-cf.bstatic.com/images/hotel/max1024x768/778/77821974.jpg">

<img src = "https://r-cf.bstatic.com/images/hotel/max1024x768/778/77822338.jpg">

<img src = "https://q-cf.bstatic.com/images/hotel/max1024x768/778/77822443.jpg">

<img src = "https://q-cf.bstatic.com/images/hotel/max1024x768/778/77822484.jpg">


<br>
<br>

# **MADRID**

## **Parador de Toledo**

Enjoying a stunning location in Cerro del Emperador, 4 km from the centre of Toledo, this Parador hotel is housed in an impressive old building and boasts magnificent views of the city.

From here, you can marvel at the views of the historical centre of Toledo, including its famous cathedral.

Parador de Turismo de Toledo combines Mudejar-style decor with contemporary touches. All rooms offer pool views. They are spacious and enjoy lots of natural light.

  * The hotel has 79 rooms. 
  * It is located 88km from Madrid Airport

<img src = "https://q-cf.bstatic.com/images/hotel/max1024x768/158/158474166.jpg">  

<img src = "https://r-cf.bstatic.com/images/hotel/max1024x768/158/158484876.jpg">

<img src = "https://q-cf.bstatic.com/images/hotel/max1024x768/158/158488297.jpg">

<img src = "https://r-cf.bstatic.com/images/hotel/max1024x768/158/158477722.jpg">

<img src = "https://q-cf.bstatic.com/images/hotel/max1024x768/158/158477599.jpg">


<br>
<br>

## **AC Ciudad de Toledo**

This hotel is set in Los Cigarrales, one of the most beautiful and emblematic areas of Toledo. It is situated next to the River Tajo and 5 minutes’ drive from the historic centre via public transport next to the hotel.

A former ceramic factory, the 4-star AC Hotel Ciudad de Toledo has been carefully renovated to respect the architectural surroundings and offers spectacular views of the city.

The hotel has extensive facilities including free WiFi throughout, as well as a gym and Turkish Bath to help you take care of body and mind.

  * The hotel has 49 rooms. So, 22 of the rooms must be triple use to fit the whole group.
  * It is located 80km from Madrid Airport
  
<img src = "https://q-cf.bstatic.com/images/hotel/max1024x768/497/49716737.jpg">  

<img src = "https://r-cf.bstatic.com/images/hotel/max1024x768/497/49716726.jpg">

<img src = "https://r-cf.bstatic.com/images/hotel/max1024x768/497/49716085.jpg"> 

<img src = "https://q-cf.bstatic.com/images/hotel/max1024x768/497/49717034.jpg"> 

<img src = "https://q-cf.bstatic.com/images/hotel/max1024x768/497/49716899.jpg"> 



*****


# **Amaze your clients!!**

<div class="client_offer">

<p>Didn't you just love our presentation ? Our first goal here at _**Cutting Edge Events**_ is to help you **win** this business. You will most likely now collate the information contained in this website and make your own presentation
to show your client<br>

<p>Why not leverage our technology, and present your client with the same format ? As a **totally free service**, we offer you the possibility of doing the work for you</p>

<p> We will: 
  <ul>
    * Follow your instructions to add anything you want to be in your presentation, and delete anything that you don't consider relevant
    * Include your logo and company details, and remove all our company details
    * We can even change some colors to mimic your corporate identity
    * We will send you the new link, and it will look as if it was your work
  </ul>
</p>
</div>

<style>

.client_offer{
background-color: #ee7600;
color: white;
padding: 10px;
border: 1px solid black;
margin-left: 5px;
border-radius: 5px;
font-style: italic;
}
</style>






